Capture and Replay Tools in the Field

### 2017-04-28 paper.tex
Minor changes from proofreading, extended summary of changes, extended conclusion

Based on their analysis, Nedyalkova and Bernardino determined that Jacareto is the best tool among the five they evaluated. Jacareto is easy to install, had better documentation, does not require additional programming skills, and supports all capture and replay characteristics except for navigation of dialog box. Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient .

@@

The experiment execution phase was split into three sessions, each composed of three tasks. These tasks were performed using the PLeTsPerf, LoadRunner  and VisualStudio approaches, one for each task, and all tasks should generate an equivalent performance test script as an output. They summarize the results by giving average time spent per treatment to complete each session. They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly .

@@

Mugshot \cite{Mickens:2010:MDC:1855711.1855722} is a deterministic capture and replay tool developed by Microsoft. It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure. To capture application activity, it records all sources of nondeterminism. If an application is run again and injected with the same non deterministic events, the program will follow the same execution path that was observed at logging time. It has its client side implemented in JavaScript to easily record logs instead of downloading additional plug-ins. For each new event it captures, it creates a log entry that contains a sequence number and wall clock time. The entry also contains the event type and enough type-specific data to recreate event at play time. Mugshot uses a caching proxy to reproduce the load events in the log . This is the limitation of Mugshot. If an application fetches external contents that does not pass through the proxy, Mugshot cannot guarantee faithful replay of its data or its load time.

\par
JARDIS \cite{paperA}, a time-traveling debugger for JavaScript. It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment . The overall system design is a record-replay-snapshot architecture. The snapshot algorithm is based on \cite{paperB} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime. 
It provides a rich set of functionality for recording and navigating the execution history of a program including: \\

@@

\section{Conclusion}
In our study, we compared four capture and replay tools, namely Reanimator, Sahi, Telerik and Selenium. The goal of this study was to determine the best tool among these which has best overall performance. These tools were compared on different criteria to find out which tool has reliable capture and replay capabilities without requiring too much human efforts. After evaluating each one of the tools, we came to a conclusion that the tool that best satisfies our requirements is Sahi. This tool stood out from rest of the tools as it has best overall performance. Therefore, we can say that Sahi can be easily adapted by any developer to test their GUI application. We also worked on Reanimator to enhance it by additing new functionalities to it. We enabled it to work on Chrome. We ...{to be added by Brian}

\section{Summary of Changes}
We expanded our study of previous work done in the field of capture and replay. We studied "Time Travel Debugging for Javascript/Node.js". This is one of the latest work in this field that allows a developer to simply press a button to step-back in a program’s execution without having developer to manually stop debugging, set a new breakpoint, and then reproduce the desired execution to hit that breakpoint.

>>>>

Based on their analysis, Nedyalkova and Bernardino determined that Jacareto is the best tool among the five they evaluated. Jacareto is easy to install, had better documentation, does not require additional programming skills, and supports all capture and replay characteristics except for navigation of dialog box. Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient.

@@

The experiment execution phase was split into three sessions, each composed of three tasks. These tasks were performed using the PLeTsPerf, LoadRunner  and VisualStudio approaches, one for each task, and all tasks should generate an equivalent performance test script as an output. They summarize the results by giving average time spent per treatment to complete each session. They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly.

@@

Mugshot \cite{Mickens:2010:MDC:1855711.1855722} is a deterministic capture and replay tool developed by Microsoft. It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure. To capture application activity, it records all sources of nondeterminism. If an application is run again and injected with the same non deterministic events, the program will follow the same execution path that was observed at logging time. It has its client side implemented in JavaScript to easily record logs instead of downloading additional plug-ins. For each new event it captures, it creates a log entry that contains a sequence number and wall clock time. The entry also contains the event type and enough type-specific data to recreate event at play time. Mugshot uses a caching proxy to reproduce the load events in the log. This is the limitation of Mugshot. If an application fetches external contents that does not pass through the proxy, Mugshot cannot guarantee faithful replay of its data or its load time.

\par
Microsoft calls JARDIS a ``time-traveling'' debugger for JavaScript. It is part of their ChakraCore JavaScript engine and a fork of the Node.js runtime environment \cite{time-travel-debugging-javascriptnode-js}. The overall system design is a record-replay-snapshot architecture. The snapshot algorithm is based on a tool called Tardis with the record-replay work done in the JsRT hosting API layer that Node.js uses to interface with the JavaScript runtime \cite{Barr:2014:TAT:2714064.2660209}.
It provides a rich set of functionality for recording and navigating the execution history of a program including: \\

@@

\section{Conclusion}
\subsection{Tool Comparison}
In our study, we compared four capture and replay tools: Reanimator, Sahi, Telerik, and Selenium. The goal of our study was to determine the best tool among these four for a developer to use in the field. We compared the four tools on different criteria to find out which tool has reliable capture and replay capabilities without requiring too much time to set up and use.
\par
After evaluating all four tools, we came to the conclusion that Sahi best satisfies our requirements. We believe that Sahi has the best overall performance and can be easily adapted by any developer to test their GUI application.
\subsection{Reanimator Extension}
We modified Reanimator with the expectation that it would be more useful for JavaScript developers to deploy to their applications in the field. We fixed bugs present in the original code to make Reanimator compatable with Google Chrome, upgraded it to support JQuery 3.2.0, and extended the functionality to allow developers to request the logs be uploaded to a server.
\par
Because the original code for Reanimator has not been modified in four years, we assumed that the developers abandoned the project. Because our version was siginificantly different from the original, we decided to not issue a pull request back to the original codebase.
\par
We believe that the original version of Reanimator was novel, but not very useful because the log was lost when a user exited his or her browser. With the addition of persistent logs (if they are being uploaded to a server), we believe that Reanimator is a very solid, lightweight capture and replay tool. We recommend that JavaScript developers implement it if they need to capture logs.
\par
We recommend adding a few more featurers to Reanimator. We recommend making the log filesizes smaller and adding a user interface for developers to help them navigate through a user's session.

\section{Summary of Changes}
\subsection{Tool Comparison}
Before our initial progress report, we had already made great progress with our analysis of different capture and replay tools. We wanted to perform the analysis early so that we could focus on the extension to Reanimator, which we viewed as the more important part of this project, since it involved creating new features that would be useful to developers.
\par
Since our initial progress report, we expanded our study of previous work done in the field of capture and replay by studying ``Time Travel Debugging for Javascript/Node.js''. This is one of the more recently developed tools in the field that allows a developer to simply press a button to step-back in a program's execution without requiring the developer to manually stop debugging, set a new breakpoint, and then reproduce the desired execution to hit that breakpoint. We were impressed with this tool.
\subsection{Reanimator Extension}
At the time of our initial progress report, we had upgraded Reanimator to work with JQuery 3.2.0. We also fixed the bugs in the code which prevented Google Chrome users from recording a session. We had to spend a significant amount of time learning how the original authors compiled the original version of Reanimator, since they left out a few important dependencies in the package.json dependency list.
\par
Since our initial progress report, we have implemented and tested the upload feature of Reanimator. We also built a new demo page to showcase the new feature.
